Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-05-15 paper/tex/analysis.tex
move analysis sentences to footnote

Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature, and each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ of the observed data is not accessible, as existing mock catalogues produce redshift-photometry pairs $(z, d)$ by a deterministic algorithm that does not correspond to a joint probability density from which one can take samples.
In these cases there is no ``true PDF'' for an individual object, and most measures of PDF fidelity will necessarily be restricted to probing the quality of the ensemble of \pzpdf s.
\boldblue{While a discrete approximation to the true $p(z,d)$ is possible by sampling the local neighbourhood of parameter space in large datasets with methods like a nearest neighbor or conditional density estimate, we do not make an explicit computation of such an approximate distribution.  Rather, we note that the CMNN and FlexZBoost algorithms are specific implementations of such algorithms which can be used as examples of such approximations in the absence of knowledge of the true $p(z,d)$.}
(See \S,\ref{sec:futureexperiments} for a discussion of how one might circumvent this limitation.)

>>>>

Galaxies have redshifts $z$ and photometric data $d$ drawn from a joint probability space $p(z, d)$ in nature, and each observed galaxy $i$ has a \textit{true posterior \pzpdf}\ $p(z \vert d_{i})$.
There are a number of metrics that can be used to test the accuracy of a \pz\ posterior as an estimator of a true \pz\ posterior if the true \pzpdf\ is known.
However, the true \pzpdf\ of the observed data is not accessible, as existing mock catalogues produce redshift-photometry pairs $(z, d)$ by a deterministic algorithm that does not correspond to a joint probability density from which one can take samples.
In these cases there is no ``true PDF'' for an individual object
\footnote{\boldblue{While a discrete approximation to the true $p(z,d)$ is possible by sampling the local neighbourhood of parameter space in large datasets with methods like a nearest neighbor or conditional density estimate, we do not make an explicit computation of such an approximate distribution.  Rather, we note that the CMNN and FlexZBoost algorithms are specific implementations of such algorithms which can be used as examples of such approximations in the absence of knowledge of the true $p(z,d)$.}}, and most measures of PDF fidelity will necessarily be restricted to probing the quality of the ensemble of \pzpdf s.
(See \S,\ref{sec:futureexperiments} for a discussion of how one might circumvent this limitation.)
